### 2025-01-16 skripsi/chapter1.tex
add outline to ch1

% \section{Sistematika Penulisan}
% \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab. Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I. Sebaiknya langsung dituliskan secara ringkas isi rincian bab-bab selanjutnya, misalnya, \textit{Setelah Pendahuluan pada Bab I ini, Bab II akan mengulas tentang ...}

>>>>

\section{Outline}
\noindent This thesis will be structured into five chapters with this chapter being the first. For further detail, \lccref{sec:literature_review} will discuss and summarize the literature related to this study. The context of the study will be explained in terms of the state of the art (SoTA), the literature involved, and how this problem fits within the larger computing and physical sciences field. In \lccref{sec:research_methodology}, we discuss the methodology that is used in this study to achieve the aims that were set in the first chapter. And then, the results of applying the research methodology are presented in \lccref{sec:results_and_discussion}. In this section, the results are also analyzed and discussed. Finally, in \lccref{sec:conclusions_and_future_work} we draw conclusions from the results and future directions of research for the use of SVMs in operator learning with basis functions.
% \noindent Bagian ini adalah penutup Bab I yang menyampaikan  secara ringkas isi setiap  bab. Karena pembaca sudah sampai akhir Bab I, yang  berarti  sudah  mengetahui isinya, maka tidak perlu ditulis lagi rincian Bab I. Sebaiknya langsung dituliskan secara ringkas isi rincian bab-bab selanjutnya, misalnya, \textit{Setelah Pendahuluan pada Bab I ini, Bab II akan mengulas tentang ...}

### 2025-01-16 skripsi/chapter4.tex
add outline to ch1

% !TEX root = ./skripsi.tex
\chapter{RESULTS AND DISCUSSION}
\noindent This chapter will elaborate on the results of the study and relevant phases for analysis. This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.

>>>>

% !TEX root = ./skripsi.tex
\chapter{RESULTS AND DISCUSSION}\label{sec:results_and_discussion}
\noindent This chapter is organized into five sections which are the results of data generation, data retrieval, design of computational model, implementation of computational model, experimental scenarios, and the experiments themselves.
